---
title: "Labels"
description: 'Label designer for multiple porpouses'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Labels}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
source("https://raw.githubusercontent.com/Flavjack/inti/master/pkgdown/favicon/docs.r")
```

# Create fieldbook

The field-book experimental design was deployed with `inti` package <https://inkaverse.com/articles/apps.html>

```{r, echo = TRUE}
library(inti)

treats <- data.frame(condition = c("irrigated", "drought")
                     , genotypes = c("choclito", "salcedo", "pandela", "puno"))

design <- tarpuy_design(data = treats
                        , nfactors = 2
                        , type = "rcbd"
                        , rep = 3
                        , barcode = "HUITO") 

fb <- design$fieldbook

fb %>% web_table()
```

# Label design

The layer options can change dynamically based in a column. In the following example the color of the text will change based in the treatments: "blue" for `irrigated` and "red" for `drought`.

> You can find more fonts in <https://fonts.google.com/>

```{r, echo = TRUE}
library(huito)

font <- c('Ceviche One', "Permanent Marker")

huito_fonts(font)

label <- fb %>% 
  mutate(color = case_when(
    condition %in% "irrigated" ~ "blue"
    , condition %in% "drought" ~ "red"
  )) %>% 
  label_layout(size = c(10, 2.5)
               , border_color = "blue"
               ) %>%
  include_image(
    value = "https://flavjack.github.io/inti/img/inkaverse.png"
    , size = c(2.4, 2.4)
    , position = c(1.2, 1.25)
    , opts = "image_scale(200)"
    ) %>%
  include_barcode(
     value = "barcode"
     , size = c(2.5, 2.5)
     , position = c(8.2, 1.25)
     ) %>%
  include_text(value = "plots"
               , position = c(9.7, 1.25)
               , angle = 90
               , size = 15
               , color = "red"
               ) %>%
  include_text(value = "Inkaverse"
               , position = c(4.6, 2)
               , size = 30
               , color = "brown"
               , font[1]
               ) %>%
  include_text(value = "condition"
               , position = c(4.6, 1.2)
               , size = 13
               , color = "color" # dynamic column
               , font[2]
               ) %>%
  include_text(value = "genotypes"
               , position = c(4.6, 0.5)
               , size = 13
               , color = "#009966"
               , font[2]
               ) 
```

You should comment `huito_fonts()` after the first running as we already imported the fonts. 

## Preview mode

The preview mode `label_print(mode = "preview")` generate a example of the label design from a random row of the data set.

```{r echo = TRUE}
label %>% 
  label_print(mode = "preview")
```

## Complete mode

If you want generate the complete labels list, change: `label_print(mode = "complete")`.

```{r echo = TRUE}
label %>% 
  label_print(mode = "complete", filename = "etiquetas", nlabels = 10)
```

<embed src="etiquetas.pdf" height="600" width="100%" alt="pdf" pluginspage="http://www.adobe.com/products/acrobat/readstep2.html">

